GBM recurrence - Shotgun proteomics analysis

### 2023-02-14 reports/gbm_recurrence_general_proteomics_manuscript_report.qmd
proteomics report - v2

---
title: "GBM recurrence - Shotgun proteomics analysis"
author: "Miguel Cosenza-Contreras"
format:
  gfm: 
    toc-depth: 4 # default is 3
    toc-title: Contents
    toc-location: left # default is right, option is 'body'
    number-sections: true
    number-depth: 3
    embed-resources: true
always_allow_html: true
editor: visual
---

>>>>

---
title: "GBM recurrence - Shotgun proteomics analysis"
author: "Miguel Cosenza-Contreras"
format:
  gfm: 
    toc-depth: 4 # default is 3
    number-sections: true
    execute:
      output: true
always_allow_html: true
editor: visual
---
